---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TFschedules

<!-- badges: start -->
<!-- badges: end -->

The goal of TFschedules is to make it easier to select teaching fellow preferences by determining which courses conflict with a given schedule. The courses considered for conflicts are obtained from html tables found on the websites for the  [CAS](http://www.bu.edu/link/bin/uiscgi_dept_class_sched?Sem=SPRG&Year=21&Col=CAS&Dept=MA) courses and [GRS](http://www.bu.edu/link/bin/uiscgi_dept_class_sched?Sem=SPRG&Year=21&Col=GRS&Dept=MA) courses.

## Installation

This package can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("RussJGoebel/TFschedules")
```
## Use

To use this app, you can run:

```{r, eval = FALSE}
TFschedules::view_schedule()

```

## Shinyapps.io

At this time, this app is running on Shinyapps.io at (https://russjgoebel.shinyapps.io/scheduleapp/).

# Updating for Future Semesters

The CAS and GRS data was obtained by hand by saving the relevant html tables in the CAS and GRS data as .txt files. 
To update the app, one method is to replace these files with updated files in the inst/Apps/ScheduleApp folder.

The `rsconnect` package can be used to update the shinyapps.io site. 


# Questions

If you have any questions, email me at rgoebel@bu.edu. 


